Legion: Expressing Locality and Independence with Logical Regions

### 2012-05-05 doc/sc2012/experiments.tex
more changes

\begin{figure}
{\footnotesize
\begin{tabular}{l|ccc}
Cluster & Sapling & Viz & Keeneland \\
\midrule
Nodes   &   4     &  10 &  32 (120) \\
CPUs/Node & 2x Xeon 5680 & 2x Xeon 5680 & 2x Xeon 5660 \\
HyperThreading & on & off & off \\
GPUs/Node & 2x Tesla C2070 & 5x Quadro Q5000 & 3x Tesla M2090 \\
DRAM/Node & 48 GB & 24 GB & 24 GB \\
Infiniband & 2x QDR & QDR & 2x QDR \\
\end{tabular}
}
\vspace{-2mm}
\caption{System configurations used for the experiments. \label{fig:systems}}
\vspace{-6mm}
\end{figure}

@@

The circuit simulation has a simple application-specific mapper.  At initialization
time, the mapper queries the list of GPUs in the machine and identifies each GPU's
framebuffer memory and {\em zero-copy} memory (pinned memory that both the GPU and
CPUs in the system can access directly).  Once the circuit is partitioned, the partitions
are assigned a home GPU in round-robin fashion.  Every task related to that partition is
then sent to the home GPU, with no task stealing allowed.  
%
% FIXME CUT
% We could put this nice sentence back in if we have space.
%
(In a well-partitioned circuit,
load imbalance is low enough that the cost of moving the private data for a piece from one
GPU to another outweighs any benefits.)
%
% FIXME CUT  
% If we find enough space this sentence and the figure can be reinserted here.
  The regions for a task are mapped as 
shown in Figure~\ref{fig:gpumapping}.

>>>>

\begin{figure}
{\footnotesize
\begin{tabular*}{3.5in}{l|ccc}
Cluster & Sapling & Viz & Keeneland \\
\midrule
Nodes   &   4     &  10 &  32 (120) \\
CPUs/Node & 2x Xeon 5680 & 2x Xeon 5680 & 2x Xeon 5660 \\
HyperThreading & on & off & off \\
GPUs/Node & 2x Tesla C2070 & 5x Quadro Q5000 & 3x Tesla M2090 \\
DRAM/Node & 48 GB & 24 GB & 24 GB \\
Infiniband & 2x QDR & QDR & 2x QDR \\
\end{tabular*}
}
\vspace{-2mm}
\caption{System configurations used for the experiments. \label{fig:systems}}
\vspace{-6mm}
\end{figure}

@@

The circuit simulation has a simple application-specific mapper.  At initialization
time, the mapper queries the list of GPUs in the machine and identifies each GPU's
framebuffer memory and {\em zero-copy} memory (pinned memory that both the GPU and
CPUs in the system can access directly).  Once the circuit is partitioned, the partitions
are assigned a home GPU in round-robin fashion.  Every task related to that partition is
then sent to the home GPU, with no task stealing allowed.  
(In a well-partitioned circuit,
load imbalance is low enough that the cost of moving the private data for a piece from one
GPU to another outweighs any benefits.)

  The regions for the tasks are mapped as 
shown in Figure~\ref{fig:gpumapping}.  Wires and private node data are kept in each GPU's
framebuffer at all times.  An instance of the ``all-shared nodes'' region is placed in
GASNet memory and instances for just the shared and ghost nodes needed by each GPU
are placed into that GPU's zero-copy memory.
